---
title: "Laboratory 1 - Introduction to R"
output: html_notebook
---

## 1.1 Introduction

The goal of this laboratory is to help you learn the most important tools in R that will allow you to do spatio-temporal data science. 

You’ll also need to install some R packages. An R package is a collection of functions, data, and documentation that extends the capabilities of base R.

You can install necessary packages with a single line of code:

```{r}
install.packages(c("tidyverse", "nycflights13", "gapminder", "Lahman"))
```

## 1.2 Running R Code

To make use of `tidyverse`, you need to run `library('tidyverse')` to load the library in the current envivronment.

```{r}
library(tidyverse)
```
### 1.2.1 The `mpg` Data Frame

Let's use our first graph to investigate whether cars with bigger engines require more fuel than those with smaller engines. You're likely aware that you already have an answer, but try to make it as accurate and precise as possible. What does the relationship between engine size and fuel efficiency show? Is it a straightforward increase in fuel consumption as engine size grows, or is there something more complex at play?

A data frame stores data in table format. You can read `mpg` data frame by simply typing the name of it:

```{r}
mpg
```

There are 11 columns in the table. Each column stores values of a variables. Among the variables in mpg are:

- `displ`, a car’s engine size, in litres.
- `hwy`, a car’s fuel efficiency on the highway, in miles per gallon (mpg). A car with a low fuel efficiency consumes more fuel than a car with a high fuel efficiency when they travel the same distance.

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
